Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for S\&R Usage

### 2022-09-15 paper/paper.tex
paper, sim result description.

    \pmb{e}(t) \\ F_1 \\ F_2

@@

\textit{agent:}\begin{enumerate}
    \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$;
    \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),$\\$ 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,$\\$0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$. Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
\end{enumerate}

\textit{UAV:}\begin{enumerate}
    \item system parameters: $g = 9.81, m = 2,
    J_x = J_y = 1.25, Jz = 2.2,
    K_x = K_y = K_z = 0.01,
    K_\phi = K_\theta = K_\psi = 0.012$
    % \item external disturbances: $d_1(t) = [ 10\sin(3t), \dots,$\\$ 10\sin(3t)] \in\mathbb{R}^6$, $f_2(t)=$
\end{enumerate}

\textit{robot:} \begin{enumerate}
    \item system parameters: Appendix E in \cite{ourrobot}
    \item designed parameters: $Q_1=,Q_2=,R=,rho=$ % correspond to x - xr, R=, \rho=$
\end{enumerate}

The simulation results of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,2}$ are given as follow.

\textit{UAV:}
The reference, state and estimated state are shown in Fig. \ref{fig:UAV, state}. The estimation of actuator fault $f_1(t)$ is shown in Fig. \ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=10\sin(3t)$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:UAV, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:UAV, control}.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:UAV, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:UAV, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:UAV, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:UAV, control}
\end{figure}

\textit{robot:}
The reference, state and estimated state are shown in Fig. \ref{fig:robot, state}. The estimation of actuator fault $f_1(t)$ is shown in Fig. \ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=\sin(3t)$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:robot, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:robot, control}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of robot walking.}%
    \label{fig:robot, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:robot, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:robot, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:robot, control}
\end{figure}

description of fig...

\section{conclusion}
In this study, a system architecture of URTS for R\&S usage is given. This gives a holistic view of the operational framework for UTRS. Next, we focus on part of the system architecture of UTRS, i.e., the reference trajectory design of UAV flying and robot walking and controller design of UAV and robot. The procedure of reference trajectory design method of UAV flying and robot walking is also given in detail. An $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) strategy is proposed to control the agent in URTS under the external disturbances. After analysis, this control problem is transformed into a LMI-constrained optimization problem. Through two-step design procedure, the problem is effectively solved by MATLAB LMI Toolbox. Finally, the effectiveness of the designed controller and observer is also verified by the simulation results. In the future, we will...

>>>>

    \pmb{e}(t) \\ F_1(t) \\ F_2(t)

@@

\textit{agents:}\begin{enumerate}
    \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$.
    \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),$\\$ 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,$\\$0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$. Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
\end{enumerate}

\textit{UAVs:}\begin{enumerate}
    \item system parameters: $g = 9.81, m = 2,
    J_x = J_y = 1.25, Jz = 2.2,
    K_x = K_y = K_z = 0.01,
    K_\phi = K_\theta = K_\psi = 0.012$. Initial values $\bar{x}_0=$.
    % \item external disturbances: $d_1(t) = [ 10\sin(3t), \dots,$\\$ 10\sin(3t)] \in\mathbb{R}^6$, $f_2(t)=$
\end{enumerate}

\textit{robots:} \begin{enumerate}
    \item system parameters: Appendix E in \cite{ourrobot}. Initial values $\bar{x}_0=$.
    \item designed parameters: $Q_1=,Q_2=,R=,rho=20$.
\end{enumerate}

The simulation results of tracking and estimation in tracking control block of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,2}$ are given as follow.

\textit{UAV:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:UAV, state}. The estimation of actuator fault $f_1(t)$ is shown in Fig. \ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=10\sin(3t)$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:UAV, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:UAV, control}.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$}%
    \label{fig:UAV, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the UAV $\alpha_{1,1}$}
    \label{fig:UAV, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of snesor fault of the UAV $\alpha_{1,1}$}%
    \label{fig:UAV, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the UAV $\alpha_{1,1}$}%
    \label{fig:UAV, control}
\end{figure}

\textit{robot:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:robot, state}. The estimation of actuator fault $f_1(t)$ is shown in Fig. \ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=\sin(3t)$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:robot, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:robot, control}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$}%
    \label{fig:robot, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:robot, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:robot, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:robot, control}
\end{figure}

In Fig. \ref{fig:UAV, state} and Fig. \ref{fig:robot, state}, the tracking and estimation errors have reached a steady state at x seconds. The transient responses that occur later are caused from fault signals, especially the sensor fault. This can be inferred from the dynamic of the estimation error (\ref{eq:e_tilde}) because the value of the sensor fault affects the value of the error over time $\dot{e}$ not only from $\bar{A}$ but also from $L\bar{C}$. In Fig \ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., disturbance and feedforward errors, can be effectively estimated. In Fig \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change, but returns to a steady state after about $3$ seconds. In Fig \ref{fig:UAV, control} and \ref{fig:robot, control}, the control effort has high frequency and high amplitude performance at the initial instance due to the high gain characteristic of the robust control, and then maintains the sine wave shape to offset the estimated actuator fault value.

\section{conclusion}
In this study, a system architecture of URTS for R\&S usage is given. This gives a holistic view of the operational framework for UTRS. Next, we focus on part of the system architecture of UTRS, i.e., the reference trajectory design of UAV flying and robot walking and controller design of UAV and robot. The procedure of reference trajectory design method of UAV flying and robot walking is also given in detail. An $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) strategy is proposed to control the agents in URTS under the external disturbances. The control problem of UAV and robot are solved together via a transformation from a general agent model. After analysis, the control problem is further transformed into a LMI-constrained optimization problem. Through two-step design procedure, the problem is effectively solved by MATLAB LMI Toolbox. The simulation results give an example of the proposed URTS architecture to more concretely illustrate its operational flow. Finally, the effectiveness of the designed controller and observer is also verified by the simulation results. In the future, we will...
